\chapter{Zemlinsky, Alexander von}
\label{cha:zemlinsky}

\href{https://en.wikipedia.org/wiki/List_of_compositions_by_Alexander_von_Zemlinsky}{List of works} on Wikipedia.





\section{Voice and Orchestra}
\noindent{Waldgespräch (T: Joseph von Eichendorff), for soprano, two horns, harp, and strings (1896)} \\
\noindent{Maiblumen blühten überall (T: Richard Dehmel), for soprano and string sextet (1899)} \\
\noindent{Erdeinsamkeit (T: unknown), for soprano and orchestra (1900-01, orchestrated by Antony Beaumont, 1999)} \\
\noindent{Der alte Garten (T: Joseph von Eichendorff), for soprano and orchestra (1900-01, orchestrated by Antony Beaumont, 1999)} \\
\noindent{Sechs Gesänge after poems by Maurice Maeterlinck, Op. 13, for soprano and orchestra (1910/13, orchestrated 1913/21)} \\
\noindent{Lyric Symphony, for soprano, baritone, and orchestra, Op. 18 (after poems by Rabindranath Tagore) (1922–23)} \textit{H\r{a}kan Hageg\r{a}rd, Alessandra Marc, KCO, Riccardo Chailly}\marginnote{high}  \\
\noindent{Symphonische Gesänge, Op. 20, for baritone or alto and orchestra (T: from Afrika singt. Eine Auslese neuer afro-amerikanischer Lyrik) (1929)} \textit{Willard White, KCO, Riccardo Chailly}\marginnote{high}  \\

\section*{Orchestral Works}
\noindent{Symphony in E minor (1891) – two surviving movements only} \\
\noindent{Symphony No. 1 in D minor (1892–93)} \\
\noindent{Eine Lustspielouvertüre (1894–95)} \\
\noindent{Symphony No. 2 in B-flat major (1897)}  \textit{Slovak PO, Edgar Seipenbusch}\marginnote{} \\
\noindent{Drei Ballettstücke. Suite from *Der Triumph der Zeit* (1902)} \\
\noindent{Die Seejungfrau (The Mermaid), fantasy after Hans Christian Andersen's "The Little Mermaid" (1902–03, premiered in Vienna in 1905)} \textit{Royal Liverpool PO< Vassili Petrenko}\marginnote{max}  \\
\noindent{Sinfonietta, Op. 23 (1934, first performance, Prague 1935)} \\

\section{Choral Works}
\noindent{Minnelied (T: Heinrich Heine) for men's choir and chamber ensemble (c.1895)} \\
\noindent{Frühlingsglaube for mixed chorus and string orchestra (T: Ludwig Uhland) (1896)} \\
\noindent{Geheimnis for mixed chorus and string orchestra (1896)} \\
\noindent{Hochzeitsgesang (T: Jewish liturgy) for Cantor (Tenor), chorus, and organ (1896), Text: Baruch Haba, Mi Adir} \\
\noindent{Frühlingsbegräbnis (Text: Paul Heyse), Cantata for soprano, baritone, mixed chorus and orchestra (1896/97, rev. c.1903)} \\
\noindent{Aurikelchen (T: Richard Dehmel) for women's choir (1898)} \\
\noindent{Psalm 83 for mixed chorus and orchestra (1900)} \textit{Slovak Philharmonic Choir, Wiener Philharmoniker, Riccardo Chailly}\marginnote{high}  \\
\noindent{Psalm 23 for chorus and orchestra, Op. 14 (1910, first performance, Vienna 1910)} \\
\noindent{Psalm 13 for chorus and orchestra, Op. 24 (1935)} \\

